---
title: "README"
output: html_document
---

# Coursera project for Getting and Cleaning Data class from JHU

## download_file.R

You should already have the original untidy dataset but by any chance if you don't,
please download the dataset by typing

```{r, eval = FALSE}
source('download_file.R')
```



## run_analysis.R

This is the main analysis script. As the given instruction by the class website, this script should perform


1. Merges the training and the test sets to create one data set.
2. Extracts only the measurements on the mean and standard deviation for each measurement. 
3. Uses descriptive activity names to name the activities in the data set
4. Appropriately labels the data set with descriptive variable names. 
5. From the data set in step 4, creates a second, 
independent tidy data set with the average of each variable
for each activity and each subject.

### run the analysis script

Please change your directory to the place where the 'run_analysis.R' file is as well as the dataset file is in './UCI HAR Dataset/'.

Then, run the following code

```{r, eval=FALSE}
source('run_analysis.R')
```


Then, you will get file, "tidy.csv", in your current directory.

The tidy dataset has subject, activity and mean, standard deviation for all features.

